Self Regulation Ontology Retest Analyses

### 2018-08-08 code/SRO_Retest_Analyses.Rmd
fixed legends for ddm figures

```{r}
tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))

ggsave('Bootstrap_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
```

@@

tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_discrete(breaks=c("Drift Rate", "Threshold", "Non-decision", "Response Time", "Accuracy"))+
  ylim(-0.4, 1)

ggsave('PointEst_DDM_Comp.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
```

>>>>

```{r}
ddm_boot_plot = tmp %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=12),
        strip.text = element_text(size=12),
        axis.text = element_text(size = 12),
        text = element_text(size=12))+
  guides(fill = guide_legend(ncol = 2, byrow=F))+
  scale_fill_brewer(palette="Greys",
                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))

mylegend<-g_legend(ddm_boot_plot)

grob_name <- names(mylegend$grobs)[1]

#manually fix the legend
#move non-decision down
#key
mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
#text
mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
#move threshold down
#key
mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
#text
mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
#move drift rate right and up
#key
mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
#text
mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)

ddm_boot_legend = arrangeGrob(ddm_boot_plot +theme(legend.position="none"),
             mylegend, nrow=2, heights=c(10, 1))

ggsave('Bootstrap_DDM_Comp_Legend.jpg', plot = ddm_boot_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 14, height = 10, units = "in", limitsize = FALSE)
```

@@

ddm_point_plot = tmp2 %>%
  ggplot(aes(factor(raw_fit, levels = c("raw", "EZ", "hddm"), labels=c("Raw", "EZ-diffusion", "Hierarchical diffusion")), icc, fill=factor(rt_acc, levels = c("rt","accuracy", "drift rate", "threshold", "non-decision"), labels=c("Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))))+
  geom_boxplot()+
  facet_wrap(~factor(contrast, levels=c("non-contrast", "contrast"), labels=c("Non-contrast", "Contrast")))+
  theme_bw()+
  ylab("ICC")+
  xlab("")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        legend.text = element_text(size=16),
        strip.text = element_text(size=16),
        axis.text = element_text(size = 16),
        text = element_text(size=16))+
  guides(fill = guide_legend(ncol = 2))+
  scale_fill_brewer(palette="Greys",
                    breaks=c( "Response Time", "Accuracy","Drift Rate", "Threshold", "Non-decision"))+
  ylim(-0.4, 1)

mylegend<-g_legend(ddm_point_plot)

grob_name <- names(mylegend$grobs)[1]

#manually fix the legend
#move non-decision down
#key
mylegend$grobs[grob_name][[1]]$layout[11,c(1:4)] <- c(4,8,4,8)
mylegend$grobs[grob_name][[1]]$layout[12,c(1:4)] <- c(4,8,4,8)
#text
mylegend$grobs[grob_name][[1]]$layout[17,c(1:4)] <- c(4,10,4,10)
#move threshold down
#key
mylegend$grobs[grob_name][[1]]$layout[9,c(1:4)] <- c(3,8,3,8)
mylegend$grobs[grob_name][[1]]$layout[10,c(1:4)] <- c(3,8,3,8)
#text
mylegend$grobs[grob_name][[1]]$layout[16,c(1:4)] <- c(3,10,3,10)
#move drift rate right and up
#key
mylegend$grobs[grob_name][[1]]$layout[7,c(1:4)] <- c(2,8,2,8)
mylegend$grobs[grob_name][[1]]$layout[8,c(1:4)] <- c(2,8,2,8)
#text
mylegend$grobs[grob_name][[1]]$layout[15,c(1:4)] <- c(2,10,2,10)

ddm_point_legend = arrangeGrob(ddm_point_plot +theme(legend.position="none"),
             mylegend, nrow=2, heights=c(10, 1))

ggsave('PointEst_DDM_Comp.jpg', plot=ddm_point_legend, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 15, height = 7, units = "in", limitsize = FALSE)
```
